Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-11 Revise-version.tex
تغییر ساختار و اضافه کردن توضیحات به روابط ریاضی

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{stfloats}
\usepackage{url}
\usepackage{booktabs,multirow, threeparttable}
\usepackage{multicol}
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{subfigure}
%\usepackage{subfig}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\begin{document}
\title{Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments}

@@

\subsection{Channel Model}
The time-domain channel impulse response between the $i$-th transmit antenna and UE follows Rayleigh fading:
\[
h_i(\tau) = \sum_{l=1}^L \alpha_{i,l} \delta(\tau-\tau_l), \quad \alpha_{i,l} \sim \mathcal{CN}(0,\sigma_l^2)
\]
where $\alpha_{i,l}$ is the complex gain and $\tau_l$ is the delay of the $l$-th path. The frequency-domain channel matrix for subcarrier $n$ is:
\[
\mathbf{H}_n = \left[H_{1,n}, H_{2,n}, \dots, H_{N_t,n}\right] \in \mathbb{C}^{1 \times N_t}
\]
with elements derived from:
\[
H_{i,n} = \sum_{l=1}^L \alpha_{i,l} e^{-j2\pi n \tau_l/N_c}
\]

@@

\begin{itemize}
    \item \textbf{SNR-Adaptive Processing}:
    \begin{equation}
        \alpha(\gamma) = 1 - e^{-\gamma/10}
    \end{equation}

    \item \textbf{Structured Latent Space}:
    \begin{equation}
        \|\mathbf{s} - \mathbf{s}'\|_2 \leq \epsilon \Rightarrow \|f_{\text{dec}}(\mathbf{s}) - f_{\text{dec}}(\mathbf{s}')\|_F \leq C\epsilon
    \end{equation}

>>>>

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{stfloats}
\usepackage{url}
\usepackage{booktabs,multirow, threeparttable}
\usepackage{multicol}
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{subfigure}
%\usepackage{subfig}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\begin{document}
\title{Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments}

@@

\subsection{Channel Model}
The time-domain channel impulse response between the $i$-th transmit antenna and UE follows Rayleigh fading:
\[
h_i(\tau) = \sum_{l=1}^L \alpha_{i,l} \delta(\tau-\tau_l), \quad \alpha_{i,l} \sim \mathcal{CN}(0,\sigma_l^2)
\]
where:
\begin{itemize}
    \item $h_i(\tau)$ is the time-domain channel impulse response for antenna $i$
    \item $\alpha_{i,l}$ is the complex gain of the $l$-th path (Rayleigh distributed)
    \item $\tau_l$ is the delay of the $l$-th path
    \item $L$ is the total number of multipath components
    \item $\mathcal{CN}(0,\sigma_l^2)$ denotes complex Gaussian distribution with variance $\sigma_l^2$
\end{itemize}
The frequency-domain channel matrix for subcarrier $n$ is:
\[
\mathbf{H}_n = \left[H_{1,n}, H_{2,n}, \dots, H_{N_t,n}\right] \in \mathbb{C}^{1 \times N_t}
\]
where:
\begin{itemize}
    \item $\mathbf{H}_n$ is the frequency-domain channel matrix for subcarrier $n$
    \item $H_{i,n}$ is the channel coefficient for antenna $i$ and subcarrier $n$
    \item $N_t$ is the number of transmit antennas
\end{itemize}
with elements derived from:
\[
H_{i,n} = \sum_{l=1}^L \alpha_{i,l} e^{-j2\pi n \tau_l/N_c}
\]

@@

\begin{itemize}
    \item \textbf{SNR-Adaptive Processing}:
    \begin{equation}
        \alpha(\gamma) = 1 - e^{-\gamma/10}
    \end{equation}
    \item \textbf{Structured Latent Space}:
    \begin{equation}
        \|\mathbf{s} - \mathbf{s}'\|_2 \leq \epsilon \Rightarrow \|f_{\text{dec}}(\mathbf{s}) - f_{\text{dec}}(\mathbf{s}')\|_F \leq C\epsilon
    \end{equation}
